True versus apparent shapes of astrophysical bow shocks

### 2016-02-06 papers/Paper1/sec-application.tex
Including circle fit figures to paper

Using the DS9 SAO image tools, we marked the positions of the proplyds and $\theta_1^C$. We followed the brightness contours along the 
bow shocks to mark the shell's position. In order to obtain the set of measurements $(R_0, R_c, D)$, we moved to the proplyd's reference frame, (where the proplyd's position)
is $(0,0)$ and measured distances in arcseconds. In this reference, the proplyd-$\theta_1^C$ line is $y=0$. With the shell's positions, we optimize a circle, whose radius is $R_c$, but
this optimization has two variants: the first one with the restriction that the center of the circle must lie in the symmetry axis (y=0), and the second variation is with no restrictions. The figure (\ref{fig:radii-measures-example}) shows a representation of the metodology described. Initially we tried to measure the radii $(R_0,R_{90})$, but it wasn't possible due to the fact that the brightness of the shell decays rapidly towards the wings, and using $R_\theta$ where $60 \lessim theta < 0 $ is not so useful, because there is not a significant difference between $R_0$ and $R_\theta$. Instead, we introduced the radius of curvature after we realized how well the shell's marks fits into a circle for all the proplyds (see figure ()).

\begin{figure*}
\begin{tabular}{cc}
\includegraphics[width=0.4\linewidth]{LV-bowshocks-xyfancy-OIII3a-LV3} & \includegraphics[width=0.4\linewidth]{LV-bowshocks-xyfancy-onaxis-OIII3a-LV3} \\
\includegraphics[width=0.4\linewidth]{LV-bowshocks-xyfancy-OIII3a-LV4} & \includegraphics[width=0.4\linewidth]{LV-bowshocks-xyfancy-onaxis-OIII3a-LV4}
\end{tabular}
\end{figure*}

>>>>

Using the DS9 SAO image tools, we marked the positions of the proplyds and $\theta_1^C$. We followed the brightness contours along the 
bow shocks to mark the shell's position. In order to obtain the set of measurements $(R_0, R_c, D)$, we moved to the proplyd's reference frame, (where the proplyd's position)
is $(0,0)$ and measured distances in arcseconds. In this reference, the proplyd-$\theta_1^C$ line is $y=0$. With the shell's positions, we optimize a circle, whose radius is $R_c$, but
this optimization has two variants: the first one with the restriction that the center of the circle must lie in the symmetry axis (y=0), and the second variation is with no restrictions. The figure (\ref{fig:radii-measures-example}) shows a representation of the metodology described. Initially we tried to measure the radii $(R_0,R_{90})$, but it wasn't possible due to the fact that the brightness of the shell decays rapidly towards the wings, and using $R_\theta$ where $60 \lesssim \theta < 0 $ is not so useful, because there is not a significant difference between $R_0$ and $R_\theta$. Instead, we introduced the radius of curvature after we realized how well the shell's marks fits into a circle for all the proplyds (see figure (\ref{fig:char-radii-obs})).

\begin{figure*}
\begin{tabular}{cc}
\includegraphics[width=0.4\linewidth]{LV-bowshocks-xyfancy-OIII3a-LV3} & \includegraphics[width=0.4\linewidth]{LV-bowshocks-xyfancy-onaxis-OIII3a-LV3} \\
\includegraphics[width=0.4\linewidth]{LV-bowshocks-xyfancy-OIII3a-LV4} & \includegraphics[width=0.4\linewidth]{LV-bowshocks-xyfancy-onaxis-OIII3a-LV4} \\
\includegraphics[width=0.4\linewidth]{LV-bowshocks-xyfancy-OIII3a-LV5} & \includegraphics[width=0.4\linewidth]{LV-bowshocks-xyfancy-onaxis-OIII3a-LV5} \\
\includegraphics[width=0.4\linewidth]{LV-bowshocks-xyfancy-OIII3a-167-328} & \includegraphics[width=0.4\linewidth]{LV-bowshocks-xyfancy-onaxis-OIII3a-167-328} \\
\includegraphics[width=0.4\linewidth]{LV-bowshocks-xyfancy-502epositions-177-341} & \includegraphics[width=0.4\linewidth]{LV-bowshocks-xyfancy-onaxis-502epositions-177-341}
\end{tabular}
\label{fig:char-radii-obs}
\caption{Fits to the shell's shapes. In the left side we have the fits without any restrictions. In the right side we have the fits restricting the center of the circle to be in $y=0$. This data is summarized in table (\ref{tab:proplyds})}
\end{figure*}
